Efficient ancestry and mutation simulation with msprime 1.0

### 2021-12-06 paper.tex

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity Science, Museum f\"ur Naturkunde Berlin, 10115, Germany }
% Castedo
\affil[9]{Fresh Pond Research Institute, Cambridge, MA 02140, USA}
% Jared, Murillo, Peter, Andy
\affil[10]{Institute of Ecology and Evolution, Department of Biology, University of Oregon, OR 97405, USA}
% Jared
\affil[11]{Computational Biology Program, Fred Hutchinson Cancer Research Center, Seattle, WA 98102, USA}
% Ariella
\affil[12]{Department of Genetics, University of North Carolina at Chapel Hill, NC 27599-7264, USA}
\affil[13]{Embark Veterinary, Inc., Boston, MA 02111, USA}
% Gregor
\affil[14]{The Roslin Institute and Royal (Dick) School of Veterinary Studies, University of Edinburgh, EH25 9RG, UK}
% Bing
\affil[15]{Institute for Genome Sciences, University of Maryland School of Medicine, Baltimore, MD, 21201, USA}
% Winni
\affil[16]{Center for Hematology and Regenerative Medicine, Karolinska Institute, 141 83 Huddinge, Sweden}
% Michael
\affil[17]{Natural History Museum, University of Oslo, Blindern 0318 Oslo, Norway}
% Simon, Dom, Ivan
\affil[18]{Department of Human Genetics, McGill University, Montr\'eal, QC H3A 0C7, Canada}
% Nathaniel
\affil[19]{Department of Entomology, Pennsylvania State University, PA 16802, USA}
% Consuelo
\affil[20]{National Laboratory of Genomics for Biodiversity (LANGEBIO), Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[21]{IIT Bombay, Powai, Mumbai 400 076, Maharashtra, India}
% Thibaut
\affil[22]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich, 85354 Freising, Germany}
% Kevin
\affil[23]{Ecology and Evolutionary Biology, University of California, Irvine, CA 92697, USA}
% Hugo
\affil[24]{No affiliation}
% Wilder 2
\affil[25]{Broad Institute of MIT and Harvard, Cambridge, MA 02142, USA}
% Jere
\affil[26]{Department of Statistics, University of Warwick, CV4 7AL, UK}
% Peter (second affil)
\affil[27]{Department of Mathematics, University of Oregon, OR 97405 USA}

>>>>

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity Science, Museum f\"ur Naturkunde Berlin, 10115, Germany }
% Castedo
\affil[9]{Fresh Pond Research Institute, Cambridge, MA 02140, USA}
% Jared, Murillo, Peter, Andy
\affil[10]{Institute of Ecology and Evolution, Department of Biology, University of Oregon, OR 97403-5289, USA}
% Jared
\affil[11]{Computational Biology Program, Fred Hutchinson Cancer Research Center, Seattle, WA 98102, USA}
% Ariella
\affil[12]{Department of Genetics, University of North Carolina at Chapel Hill, NC 27599-7264, USA}
\affil[13]{Embark Veterinary, Inc., Boston, MA 02111, USA}
% Gregor
\affil[14]{The Roslin Institute and Royal (Dick) School of Veterinary Studies, University of Edinburgh, EH25 9RG, UK}
% Bing
\affil[15]{Institute for Genome Sciences, University of Maryland School of Medicine, Baltimore, MD, 21201, USA}
% Winni
\affil[16]{Center for Hematology and Regenerative Medicine, Karolinska Institute, 141 83 Huddinge, Sweden}
% Michael
\affil[17]{Natural History Museum, University of Oslo, Blindern 0318 Oslo, Norway}
% Simon, Dom, Ivan
\affil[18]{Department of Human Genetics, McGill University, Montr\'eal, QC H3A 0C7, Canada}
% Nathaniel
\affil[19]{Department of Entomology, Pennsylvania State University, PA 16802, USA}
% Consuelo
\affil[20]{National Laboratory of Genomics for Biodiversity (LANGEBIO), Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[21]{IIT Bombay, Powai, Mumbai 400 076, Maharashtra, India}
% Thibaut
\affil[22]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich, 85354 Freising, Germany}
% Kevin
\affil[23]{Ecology and Evolutionary Biology, University of California, Irvine, CA 92697, USA}
% Hugo
\affil[24]{No affiliation}
% Wilder 2
\affil[25]{Broad Institute of MIT and Harvard, Cambridge, MA 02142, USA}
% Jere
\affil[26]{Department of Statistics, University of Warwick, CV4 7AL, UK}
% Peter (second affil)
\affil[27]{Department of Mathematics, University of Oregon, OR 97403-5289 USA}
